Formation of $\cenn$ Molecules in Oxygen-rich Interiors of Type II Supernovae

### 2013-03-14 doc/submit/ms.tex
Minor text change.

Figure \ref{fig:yi}
shows the abundances $Y_i$ of each species in our small network as a
function of time $t-t(6000 {\rm K})$ after $T=6000$ K.
From Table \ref{tab:quantities},
start time is $t(6000K) =5.47 \times 10^6$ s.
To display each $Y_i$ on a figure with
reasonable ordinate resolution, we have scaled each $Y_n$\ by the factor
stated in the box. Many features are noteworthy: (1) $Y_C$ and $Y_O$ 
are constant
because their small depletion is negligible on the scale shown;
(2) maxima of $Y_{CO}$ and $Y_2$\ occur at almost exactly the same time
$t-t(6000K)= 4 \times 10^6$ s, as was also seen in Fig. \ref{fig:ncoc2};
(3) $\cthree$\ has very small abundance, about $10^{-7}$ of $Y_2$\
at the $Y_2$\ maximum, although much later $Y_3$\ slowly grows modestly
relative to much more abundant $\ctwo$; (4) the rise shapes of $Y_4$
through $Y_8$\ are very similar because they are linked by a near steady
state; (5) the ringed carbon $Y(\ceightr$) has similar abundance shape vs. time,
but notice that it is actually much more abundant than lineaer $C_{7-8}$ and
because it accumulates from isomeric transitions of $\ceight$\
and unlike $\cenn$\ does not
suffer from fast oxidation \citep{1999Sci...283.1290C}. Each of these
features is understandable in terms of the flows into and out of each species.

@@

\bibitem[{{Cherchneff} \& {Dwek}(2009)}]{2009ApJ...703..642C}
{Cherchneff}, I. \& {Dwek}, E. 2009, \apj, 703, 642

>>>>

Figure \ref{fig:yi}
shows the abundances $Y_i$ of each species in our small network as a
function of time $t-t(6000 {\rm K})$ after $T=6000$ K.
From Table \ref{tab:quantities},
start time is $t(6000K) =5.47 \times 10^6$ s.
To display each $Y_i$ on a figure with
reasonable ordinate resolution, we have scaled each $Y_n$\ by the factor
stated in the box. Many features are noteworthy: (1) $Y_C$ and $Y_O$ 
are constant
because their small depletion is negligible on the scale shown;
(2) maxima of $Y_{CO}$ and $Y_2$\ occur at almost exactly the same time
$t-t(6000K)= 4 \times 10^6$ s, as was also seen in Fig. \ref{fig:ncoc2};
(3) $\cthree$\ has very small abundance, about $10^{-7}$ of $Y_2$, 
although much later $Y_3$\ slowly grows modestly
relative to much more abundant $\ctwo$; (4) the rise shapes of $Y_4$
through $Y_8$\ are very similar because they are linked by a near steady
state; (5) the ringed carbon $Y(\ceightr$) has similar abundance shape vs. time,
but notice that it is actually much more abundant than lineaer $C_{7-8}$ and
because it accumulates from isomeric transitions of $\ceight$\
and unlike $\cenn$\ does not
suffer from fast oxidation \citep{1999Sci...283.1290C}. Each of these
features is understandable in terms of the flows into and out of each species.

@@

\bibitem[{{Cherchneff} \& {Dwek}(2009)}]{2009ApJ...703..642C}
{Cherchneff}, I. \& {Dwek}, E. 2009, \apjl, 703, 642
